Context Inconsistency Management \\in Pervasive Systems

### 2011-04-07 paper/paper.tex
minor tweaks

Interestingly a fuzzy ontology has some tree-like structure that allows for very efficient incremental partial probability calculation (PPC). The probability of a higher-level context is calculated by simply multiplying the probabilities of the observed contexts. When a new context is added to the observation window, the intermediate calculation result stored at a node (the root in our case study) can simply be multiplied by the probability of the new observation in order to obtain the updated probability for a higher-level context. When a context disappears from the observation window, the intermediate result can simply be divided by the context's probability to obtain an updated probability for a higher-level context.

@@

Then we have shown examples of CCTs of entities in an ontology based context model. We have not shown an algorithm on how to do this efficiently as we don't know the formal definition of OWL at this point in time. However, with the definitions of OWL one can create a depth-first search algorithm that transforms an ontology in multiple CCTs (one for each leaf entity in the model).

After that we shed light on ways to resolve the detected conflicts and discussed a context inconsistency resolution algorithm that estimates the reliability of conflicting contexts and only retains the most reliable context from every conflict set. Using this algorithm allows for timely conflict resolution at runtime without the need for human participation. The algorithm is a valuable addition to the research on conflict resolution in pervasive computing, but when applying it one has to verify the aptness of the heuristic used for context reliability estimations in the domain at hand. In particular the assumption that contexts with the highest relative frequency are most reliable has to apply in the domain.

>>>>

Interestingly a fuzzy ontology has some tree-like structure which allows for very efficient incremental partial probability calculation (PPC). The probability of a higher-level context is calculated by simply multiplying the probabilities of the observed contexts. When a new context is added to the observation window, the intermediate calculation result stored at a node (the root in our case study) can simply be multiplied by the probability of the new observation in order to obtain the updated probability for a higher-level context. When a context disappears from the observation window, the intermediate result can simply be divided by the context's probability to obtain an updated probability for a higher-level context.

@@

Then we have shown examples of CCTs of entities in an ontology based context model. We have not shown an algorithm on how to do this efficiently as we don't know the formal definition of OWL at this point in time. However, with the definitions of OWL one can create a depth-first search algorithm which transforms an ontology in multiple CCTs (one for each leaf entity in the model).

After that we shed light on ways to resolve the detected conflicts and discussed a context inconsistency resolution algorithm which estimates the reliability of conflicting contexts and only retains the most reliable context from every conflict set. Using this algorithm allows for timely conflict resolution at runtime without the need for human participation. The algorithm is a valuable addition to the research on conflict resolution in pervasive computing, but when applying it one has to verify the aptness of the heuristic used for context reliability estimations in the domain at hand. In particular the assumption that contexts with the highest relative frequency are most reliable has to apply in the domain.
